
\acknowledgements
\setcode{utf8}
\begin{arabtext}
\centerline{بِسْمِ اللَّهِ الرَّحْمَنِ الرَّحِيمِ }  
\end{arabtext}
 \hfill \break
 
The Ph.D. journey I had in the past three years have faced many challenges and obstacles on research-wise, personal wise, and on my overall lifestyle. Without the immense support I had from many kindred minds and colleagues that shared parts of this journey over research lab, meetings and ideation sessions, or coffee, whom to I am heartily thankful. 

First and foremost I would like to thank my supervisor and superhuman prof. Kouta Minamizawa for his great support and encouragement, and providing me the needed environment for conducting my research freely.

Also, I owe great gratitude to my thesis co-supervisors: prof. Hideki Sunahara, prof. Keiko Okawa, prof. Naohito Okude, and prof. Susumu Tachi for their great iterative feedback, helping me constructing my thesis thoroughly and logically. Highlighting prof. Okude's continues challenges that, by all means, reflected a great deal improving my writing style. Great gratitude goes to prof. Tachi who involved me in the Telexistence project, which I worked with for the past six years. 

Also, I would like to thank external reviewers: prof. Kai Kuzne, Tilman Dingler, prof. Mathew Waldman, and Roshan Peiris who kindly spared some of their time to read, criticize, and giving me feedback of my written work. And for the support I received from prof. Masahiko Inami on both academic and professional level.

I also owe a great debt of gratitude to many friends and colleagues in my laboratory and beyond who supported me while conducting my research and writing my thesis. I would like to highlight few out of many of these amazing people on this list. Emily Kojima was more like our spiritual guardian who handled most of the administrative and bureaucratic procedures, which made our life smooth and productive, also for her constant positivity and support. Also for Mina Shibasaki's help during tough Japanese related matters, and helping me find the light in the world of Kanjis. For the time with Kevin Fan's discussing several research topics and ideas. For the amazing technical help I received from Youichi Kamiyama during some of the projects I worked on. For Tomoya Sasaki's constant support in research, demonstrations, and work during MetaLimbs project. And for Reo Matsumura's professionalism during our work on the development of Embodiment Toolkit. And, I would like to thank my colleagues whom I have worked with in Tachilab Telexistence projects. 

I would also dedicate a gratitude to Norikazu Takagi and his grandmother for the work we had on the HUG Project and Pepper App Challenge. The immense experience I had while conducting this project reflected the importance of deploying our research for the well-being of our society.

This research has required several expensive equipments and financial support for conference submissions and attendance, which was kindly received by Japan Science and Technology Agency (JST)'s Kakenhi and Accel funds. Also for the support received by NEDO while conducting Telexistence base Surveillance System project. 

Finally, to adequately conclude my acknowledgment, my gratitude and thankfulness go to my parents: Moneer and Sawsan, and my siblings: Khaled, Shaza, and Ahmed for their constant spiritual and emotional support that helped me carry on the persuade of Ph.D. degree. 
