% Appendix
\pagebreak
\chapter{EDD Related Publications}

\section{Conference Papers}
\subsection{International Conferences}

\footnotesize
\begin{enumerate}
\item \textbf{MHD Yamen Saraiji}, Charith Fernando, Masahiro Furukawa, Kouta Minarnizawa, and Susumu Tachi. \textit{``Real-time egocentric superimposition of operator's own body on telexistence avatar in virtual environment.''} In Artificial Reality and Telexistence (ICAT), 2013 23rd International Conference on, pp. 35-39. IEEE, 2013.

\item  \textbf{MHD Yamen Saraiji}, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Development of Mutual Telexistence System using Virtual Projection of Operator's Egocentric Body Images.''} In ICAT-EGVE, pp. 125-132. 2015.


\item \textbf{MHD Yamen Saraiji}, Shota Sugimoto, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Layered telepresence: simultaneous multi presence experience using eye gaze based perceptual awareness blending.''} In ACM SIGGRAPH 2016 Posters, p. 20. ACM, 2016.

\item \textbf{MHD Yamen Saraiji}, Shota Sugimoto, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Layered telepresence: simultaneous multi presence experience using eye gaze based perceptual awareness blending.''} In ACM SIGGRAPH 2016 Posters, p. 20. ACM, 2016.

\item \textbf{MHD Yamen Saraiji}, Yusuke Mizushina, Charith Fernando, Masahiro Furukawa, Youichi Kamiyama, Kouta Minamizawa, and Susumu Tachi. \textit{``Enforced telexistence.''} In ACM SIGGRAPH 2014 Posters, p. 49. ACM, 2014.

\end{enumerate}

\subsection{Domestic Conferences}

\begin{enumerate}
\item \textbf{MHD Yamen Saraiji}, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Study on Telexistence LXXXV Layered Presence: Expanding Visual Presence using Simultaneously Operated Telexistence Avatars.''} In Virtual Reality Society of Japan (2016).

\item \textbf{MHD Yamen Saraiji}, Kouta Minamizawa, and Susumu Tachi. \textit{``Study on Telexistence LXXXVIII Foveated Streaming: Optimizing video streaming for Telexistence systems\\ using eye-gaze based foveation.''} In Virtual Reality Society of Japan (2017).

\end{enumerate}


\section{Demonstrations}

\begin{enumerate}
\item \textbf{MHD Yamen Saraiji}, Charith Fernando, Yusuke Mizushina, Youichi Kamiyama, Kouta Minamizawa, and Susumu Tachi. \textit{``Enforced telexistence: teleoperating using photorealistic virtual body and haptic feedback.''} In SIGGRAPH Asia 2014 Emerging Technologies, p. 7. ACM, 2014.

\item \textbf{MHD Yamen Saraiji}, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Mutual hand representation for telexistence robots using projected virtual hands.''} In Proceedings of the 6th Augmented Human International Conference, pp. 221-222. ACM, 2015.

\item  \textbf{MHD Yamen Saraiji}, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Development of Mutual Telexistence System using Virtual Projection of Operator's Egocentric Body Images.''} In ICAT-EGVE, pp. 125-132. 2015.

\item \textbf{MHD Yamen Saraiji}, Shota Sugimoto, Charith Fernando, Kouta Minamizawa, and Susumu Tachi. \textit{``Layered telepresence: simultaneous multi presence experience using eye gaze based perceptual awareness blending.''} In ACM SIGGRAPH 2016 Emerging Technologies, ACM, 2016.

\item Tomoya Sasaki, \textbf{MHD Yamen Saraiji}, Charith Fernando, Kouta Minamizawa, and Masahiko Inami. \textit{``MetaLimbs: Metamorphosis for multiple arms interaction using artificial limbs.''} In 44th International Conference on Computer Graphics and Interactive Techniques, ACM SIGGRAPH 2017. Association for Computing Machinery, Inc, 2017.

\end{enumerate}

\section{Awards}

\begin{enumerate}
\item Best Demo Award, \textit{``Mutual hand representation for telexistence robots using projected virtual hands.''} In Proceedings of the 6th Augmented Human International Conference, pp. 221-222. ACM, 2015.
\item Honorable Mention \& Best Demo Award, \textit{``Development of Mutual Telexistence System using Virtual Projection of Operator's Egocentric Body Images.''} In ICAT-EGVE, pp. 125-132. 2015.

\item Best in Show \& Best Care and Welfare Project award, \textit{``HUG Project.''} In Pepper App Challenge 2015.

\item Best Research Presentation award, \textit{``Study on Telexistence LXXXV Layered Presence: Expanding Visual Presence using Simultaneously Operated Telexistence Avatars.''} In Virtual Reality Society of Japan (2016).

\item Student Research Competition Gold Prize, \textit{``Layered telepresence: simultaneous multi presence experience using eye gaze based perceptual awareness blending.''} In SIGGRAPH 2017

\item Best in Show award, \textit{``MetaLimbs: Metamorphosis for multiple arms interaction using artificial limbs.''} In SIGGRAPH 2017

\end{enumerate}


%\subsection{Press}
%\begin{enumerate}
%\item \textit{HUG Project 2015} https://hugproject.net/ .
%\end{enumerate}